---
title: "Tennis Visualization Coke's Serve"
author: "Brian Dinh"
date: "2024-03-12"
output: html_document
---

# PLEASE RUN THE LAST COMMAND INTO YOUR CONSOLE TO GET THE IMAGE




# Libraries
```{r}
library(png)
library(readr)
library(dplyr)
library(grid)
library(ggplot2)
library(ggpubr)
library(ggtext)
library(reshape)
library(reshape2)
library(zoo)
library(gt)
library(scales)
library(MASS)
library("formattable")

```

# Loading in Data
```{r}
pointdata <- read.csv("Point_Visuals_SpencerJohnson_AlessioBasile.csv")
shotdata <- read.csv("Shot_Visuals_SpencerJohnson_AlessioBasile.csv")

# Assuming pointdata is a data frame or list containing player names
player1 <- pointdata$player1Name[1]
player2 <- pointdata$player2Name[1]

grid1 <- readPNG("Tennis_Court_Dark_With_Background_Half.png")

```


# Merging the Data
```{r}
# Merge Data
example_df <- pointdata[, c('pointWonBy', 'pointNumber','player1ServePlacement')]

colnames(example_df)[colnames(example_df) == 'pointWonBy'] <- 'pointWonBy_PV'
shot_merged <- merge(shotdata, example_df, by='pointNumber')

cat("Checking which points are not marked in pointWonBy_PV...\n") # : ", which(shot_merged["pointWonBy_PV"] == ""))
if (length(which(shot_merged["pointWonBy_PV"] == "")) == 0) {
  cat("Check Passed! ✔")
} else {
  which(shot_merged["pointWonBy_PV"] == "")
}
#View(shot_merged)
```




# Finding Serve + 1 Data
```{r}
# View(pointdata)
# View(shotdata)
# need to find where he serves on Deuce, then hits "Down the Line" -> look at win% , then we can find "Crosscourt" -> look at win%
# need to find where he serves on Ad, then he hits "Down the Line"\

# if the side is blank
  for (i in 1:nrow(shot_merged)){
    if (shot_merged[i, "side"] == "") {
      if (shot_merged[i-1, "shotInRally"] == 1){
        shot_merged[i, "side"] <- shot_merged[i -1 , "side"]
      }
      
      # If return is Ad and Crosscourt
      else if (shot_merged[i-1, "side"] == "Ad" & shot_merged[i-1, "shotDirection"] == "Crosscourt") {
        shot_merged[i, "side"] <- "Ad"
      }
      # if return is Ad and Down the Line  
      else if (shot_merged[i-1, "side"] == "Ad" & shot_merged[i-1, "shotDirection"] == "Down the Line") {
        shot_merged[i, "side"] <- "Deuce"
      }
      # If return is Deuce and Cross Court
     else if (shot_merged[i-1, "side"] == "Deuce" & shot_merged[i-1, "shotDirection"] == "Crosscourt") {
        shot_merged[i, "side"] <- "Deuce"
     }
      # If return is Deuce and Down the Line
      else if (shot_merged[i-1, "side"] == "Deuce" & shot_merged[i-1, "shotDirection"] == "Down the Line") {
        shot_merged[i, "Side"] <- "Ad"
      }
    }
  }
cat("Checking if shot in rally is blank....\n") # \nCheck: ", which(shot_merged["side"] == ""))
if (length(which(shot_merged["side"] == "")) == 0) {
  cat("Check Passed! ✔")
} else {
  which(shot_merged["side"] == "")
}
# View(shot_merged)

```



# Getting Change of Dir After Serving Deuce (Hitting to Ad Side)
```{r}
# Correct Index
## Getting a list of the third rally shots after player serves on Deuce T
servingDeuceT <- shot_merged %>%
  group_by(pointNumber) %>% slice(3) %>% filter(serverName == player1, grepl("Deuce: T", player1ServePlacement))

## Getting a list of the third rally shots after player serves on Deuce Body
servingDeuceBody <- shot_merged %>%
  group_by(pointNumber) %>% slice(3) %>% filter(serverName == player1, grepl("Deuce: Body", player1ServePlacement))

### Getting a list of the third rally shots after player serves on Deuce Wide
servingDeuceWide <- shot_merged %>%
  group_by(pointNumber) %>% slice(3) %>% filter(serverName == player1, grepl("Deuce: Wide", player1ServePlacement))



## Getting the count of all shots that were change of direction to Ad side after serving Deuce T ("Deuce: DTL" AND "Ad: Crosscourt")
servingDeuceT_changedir_count <-sum( ((servingDeuceT["side"] == "Deuce" & servingDeuceT["shotDirection"] == "Down the Line") | (servingDeuceT["side"] == "Ad" & servingDeuceT["shotDirection"] == "Crosscourt")))


## Getting the count of all shots that were change of direction to Ad side after serving Deuce Body ("Deuce: DTL" AND "Ad: Crosscourt")
servingDeuceBody_changedir_count <-sum( ((servingDeuceBody["side"] == "Deuce" & servingDeuceBody["shotDirection"] == "Down the Line") | (servingDeuceBody["side"] == "Ad" & servingDeuceBody["shotDirection"] == "Crosscourt")))


## Getting the count of all shots that were change of direction to Ad side after serving Deuce Wide ("Deuce: DTL" AND "Ad: Crosscourt")
servingDeuceWide_changedir_count <-sum( ((servingDeuceWide["side"] == "Deuce" & servingDeuceWide["shotDirection"] == "Down the Line") | (servingDeuceWide["side"] == "Ad" & servingDeuceWide["shotDirection"] == "Crosscourt")))


##### Getting count of when they won now #####


## Getting the count of all shots that were change of direction to Ad side after serving Deuce T ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON 
servingDeuceT_changedir_won_count <- sum( ((servingDeuceT["side"] == "Deuce" & servingDeuceT["shotDirection"] == "Down the Line") | (servingDeuceT["side"] == "Ad" & servingDeuceT["shotDirection"] == "Crosscourt"))  & servingDeuceT["pointWonBy_PV"] == player1)


## Getting the count of all shots that were change of direction to Ad Side after serving Deuce Body ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON
servingDeuceBody_changedir_won_count <- sum( ((servingDeuceBody["side"] == "Deuce" & servingDeuceBody["shotDirection"] == "Down the Line") | (servingDeuceBody["side"] == "Ad" & servingDeuceBody["shotDirection"] == "Crosscourt"))  & servingDeuceBody["pointWonBy_PV"] == player1)


## Getting the count of all shots that were change of direction to Ad Side after serving Deuce Wide ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON
servingDeuceWide_changedir_won_count <- sum( ((servingDeuceWide["side"] == "Deuce" & servingDeuceWide["shotDirection"] == "Down the Line") | (servingDeuceWide["side"] == "Ad" & servingDeuceWide["shotDirection"] == "Crosscourt"))  & servingDeuceWide["pointWonBy_PV"] == player1)
```


## No Change of Direction After Serving Deuce (Hitting to Deuce Side)
```{r}
## Getting the count of all shots that were NOT change of direction after serving Deuce T ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingDeuceT_nochange_count <-sum( ((servingDeuceT["side"] == "Deuce" & servingDeuceT["shotDirection"] == "Crosscourt") | (servingDeuceT["side"] == "Ad" & servingDeuceT["shotDirection"] == "Down the Line")))


## Getting the count of all shots that were NOT change of direction after serving Deuce Body ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingDeuceBody_nochange_count <-sum( ((servingDeuceBody["side"] == "Deuce" & servingDeuceBody["shotDirection"] == "Crosscourt") | (servingDeuceBody["side"] == "Ad" & servingDeuceBody["shotDirection"] == "Down the Line")))


## Getting the count of all shots that were NOT change of direction after serving Deuce Wide ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingDeuceWide_nochange_count <-sum( ((servingDeuceWide["side"] == "Deuce" & servingDeuceWide["shotDirection"] == "Crosscourt") | (servingDeuceWide["side"] == "Ad" & servingDeuceWide["shotDirection"] == "Down the Line")))


##### Getting count of when they won now #####


## Getting the count of all shots that were NOT change of direction after serving Deuce T ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingDeuceT_nochange_won_count <- sum( ((servingDeuceT["side"] == "Deuce" & servingDeuceT["shotDirection"] == "Crosscourt") | (servingDeuceT["side"] == "Ad" & servingDeuceT["shotDirection"] == "Down the Line"))  & servingDeuceT["pointWonBy_PV"] == player1)


## Getting the count of all shots that were NOT change of direction after serving Deuce Body ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingDeuceBody_nochange_won_count <- sum( ((servingDeuceBody["side"] == "Deuce" & servingDeuceBody["shotDirection"] == "Crosscourt") | (servingDeuceBody["side"] == "Ad" & servingDeuceBody["shotDirection"] == "Down the Line")) & servingDeuceBody["pointWonBy_PV"] == player1)


## Getting the count of all shots that were NOT change of direction after serving Deuce Wide ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingDeuceWide_nochange_won_count <- sum( ((servingDeuceWide["side"] == "Deuce" & servingDeuceWide["shotDirection"] == "Crosscourt") | (servingDeuceWide["side"] == "Ad" & servingDeuceWide["shotDirection"] == "Down the Line"))  & servingDeuceWide["pointWonBy_PV"] == player1)
```








# Getting Change of Dir After Serving Ad (Hitting to Deuce Side)
```{r}
# Correct Index
## Getting a list of the third rally shots after player serves on Ad T
servingAdT <- shot_merged %>%
  group_by(pointNumber) %>% slice(3) %>% filter(serverName == player1, grepl("Ad: T", player1ServePlacement))

## Getting a list of the third rally shots after player serves on Ad Body
servingAdBody <- shot_merged %>%
  group_by(pointNumber) %>% slice(3) %>% filter(serverName == player1, grepl("Ad: Body", player1ServePlacement))

## Getting a list of the third rally shots after player serves on Ad Wide
servingAdWide <- shot_merged %>%
  group_by(pointNumber) %>% slice(3) %>% filter(serverName == player1, grepl("Ad: Wide", player1ServePlacement))




## Getting the count of all shots that were change of direction to Deuce side after serving Ad T("Ad: DTL" AND "Deuce: Crosscourt")
servingAdT_changedir_count <-sum( ((servingAdT["side"] == "Ad" & servingAdT["shotDirection"] == "Down the Line") | (servingAdT["side"] == "Deuce" & servingAdT["shotDirection"] == "Crosscourt")))


## Getting the count of all shots that were change of direction to Deuce side after serving Ad Body ("Deuce: DTL" AND "Ad: Crosscourt")
servingAdBody_changedir_count <-sum( ((servingAdBody["side"] == "Ad" & servingAdBody["shotDirection"] == "Down the Line") | (servingAdBody["side"] == "Deuce" & servingAdBody["shotDirection"] == "Crosscourt")))


## Getting the count of all shots that were change of direction to Deuce side after serving Ad Wide ("Deuce: DTL" AND "Ad: Crosscourt")
servingAdWide_changedir_count <-sum( ((servingAdWide["side"] == "Ad" & servingAdWide["shotDirection"] == "Down the Line") | (servingAdWide["side"] == "Deuce" & servingAdWide["shotDirection"] == "Crosscourt")))


##### Getting count of when they won now #####


## Getting the count of all shots that were change of direction to Deuce Side after serving Ad T ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON
servingAdT_changedir_won_count <- sum( ((servingAdT["side"] == "Ad" & servingAdT["shotDirection"] == "Down the Line") | (servingAdT["side"] == "Deuce" & servingAdT["shotDirection"] == "Crosscourt"))  & servingAdT["pointWonBy_PV"] == player1)


## Getting the count of all shots that were change of direction to Deuce Side after serving Ad Body ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON
servingAdBody_changedir_won_count <- sum( ((servingAdBody["side"] == "Ad" & servingAdBody["shotDirection"] == "Down the Line") | (servingAdBody["side"] == "Deuce" & servingAdBody["shotDirection"] == "Crosscourt"))  & servingAdBody["pointWonBy_PV"] == player1)

## Getting the count of all shots that were change of direction to Deuce Side after serving Ad Wide ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON
servingAdWide_changedir_won_count <- sum( ((servingAdWide["side"] == "Ad" & servingAdWide["shotDirection"] == "Down the Line") | (servingAdWide["side"] == "Deuce" & servingAdWide["shotDirection"] == "Crosscourt"))  & servingAdWide["pointWonBy_PV"] == player1)

```


## No Change of Direction After Serving Ad (Hitting to Ad Side)
```{r}
## Getting the count of all shots that were NOT change of direction after serving Ad T ("Deuce: Down the Line" AND "Ad: Crosscourt")
servingAdT_nochange_count <-sum( ((servingAdT["side"] == "Deuce" & servingAdT["shotDirection"] == "Down the Line") | (servingAdT["side"] == "Ad" & servingAdT["shotDirection"] == "Crosscourt")))


## Getting the count of all shots that were NOT change of direction after serving Deuce Body ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingAdBody_nochange_count <-sum( ((servingAdBody["side"] == "Deuce" & servingAdBody["shotDirection"] == "Down the Line") | (servingAdBody["side"] == "Ad" & servingAdBody["shotDirection"] == "Crosscourt")))


## Getting the count of all shots that were NOT change of direction after serving Deuce Wide ("Deuce: Crosscourt" AND "Ad: Down the Line")
servingAdWide_nochange_count <-sum( ((servingAdWide["side"] == "Deuce" & servingAdWide["shotDirection"] == "Down the Line") | (servingAdWide["side"] == "Ad" & servingAdWide["shotDirection"] == "Crosscourt")))


##### Getting count of when they won now #####


## Getting the count of all shots that were NOT change of direction after serving Ad T ("Deuce: Crosscourt" AND "Ad: Down the Line")& where player1 WON 
servingAdT_nochange_won_count <- sum( ((servingAdT["side"] == "Deuce" & servingAdT["shotDirection"] == "Down the Line") | (servingAdT["side"] == "Ad" & servingAdT["shotDirection"] == "Crosscourt"))  & servingAdT["pointWonBy_PV"] == player1)


## Getting the count of all shots that were NOT change of direction after serving Ad Body ("Deuce: Crosscourt" AND "Ad: Down the Line")& where player1 WON 
servingAdBody_nochange_won_count <- sum( ((servingAdBody["side"] == "Deuce" & servingAdBody["shotDirection"] == "Down the Line") | (servingAdBody["side"] == "Ad" & servingAdBody["shotDirection"] == "Crosscourt")) & servingAdBody["pointWonBy_PV"] == player1)


## Getting the count of all shots that were change of direction to Ad Side after serving Deuce Wide ("Deuce: DTL" AND "Ad: Crosscourt") & where player1 WON
servingAdWide_nochange_won_count <- sum( ((servingAdWide["side"] == "Deuce" & servingAdWide["shotDirection"] == "Down the Line") | (servingAdWide["side"] == "Ad" & servingAdWide["shotDirection"] == "Crosscourt"))  & servingAdWide["pointWonBy_PV"] == player1)
```



# Making it Into A Data Frame   
```{r}

serveplus1 <- data.frame(
  
    "DeuceT" = c(paste0(servingDeuceT_changedir_won_count, "/", servingDeuceT_changedir_count),
            paste0(servingDeuceT_nochange_won_count, "/", servingDeuceT_nochange_count), 
            paste0(round((servingDeuceT_changedir_won_count + servingDeuceT_nochange_won_count) / (servingDeuceT_changedir_count + servingDeuceT_nochange_count),2) * 100,"%")),
  
  "DeuceBody" = c(paste0(servingDeuceBody_changedir_won_count, "/", servingDeuceBody_changedir_count),
            paste0(servingDeuceBody_nochange_won_count, "/", servingDeuceBody_nochange_count),
            paste0(round((servingDeuceBody_changedir_won_count + servingDeuceBody_nochange_won_count) / (servingDeuceBody_changedir_count + servingDeuceBody_nochange_count ),2) * 100,"%")),
  
  "DeuceWide" = c(paste0(servingDeuceWide_changedir_won_count, "/", servingDeuceWide_changedir_count),
            paste0(servingDeuceWide_nochange_won_count, "/", servingDeuceWide_nochange_count),  
            paste0(round((servingDeuceWide_changedir_won_count + servingDeuceWide_nochange_won_count)/ (servingDeuceWide_changedir_count + servingDeuceWide_nochange_won_count),2) * 100,"%")),
  "AdT" = c(paste0(servingAdT_changedir_won_count, "/", servingAdT_changedir_count),
            paste0(servingAdT_nochange_won_count, "/", servingAdT_nochange_count),
            paste0(round((servingAdT_changedir_won_count + servingAdT_nochange_won_count) / (servingAdT_changedir_count + servingAdT_nochange_count),2) * 100,"%")),
  
  "AdBody" = c(paste0(servingAdBody_changedir_won_count, "/", servingAdBody_changedir_count),
            paste0(servingAdBody_nochange_won_count, "/", servingAdBody_nochange_count),
            paste0(round((servingAdBody_changedir_won_count + servingAdBody_nochange_won_count) / (servingAdBody_changedir_count + servingAdBody_nochange_count),2) * 100,"%")),
  
  "AdWide" = c(paste0(servingAdWide_changedir_won_count, "/", servingAdWide_changedir_count),
            paste0(servingAdWide_nochange_won_count, "/", servingAdWide_nochange_count), 
            paste0(round((servingAdWide_changedir_won_count + servingAdWide_nochange_won_count) / (servingAdWide_changedir_count + servingAdWide_nochange_count),2) * 100,"%")),
  check.names = FALSE
  
)

rownames(serveplus1) <- c("Serve + 1 (Change Direction)","Serve + 1 (No Change Direction)", "Win %")

gtserveplus1 <- serveplus1 %>%
   gt(rownames_to_stub = TRUE) %>%
  tab_header(title=md("**Serve + 1**"), subtitle = NULL, preheader = NULL) %>%
   cols_label(DeuceT = 'T', DeuceBody = 'Body', DeuceWide = 'Wide', 
              AdT = 'T', AdBody = 'Body', AdWide = 'Wide') %>%
   tab_spanner(
    label = "Deuce Serves",
    columns = 2:4) %>%
    tab_spanner(
      label = "Ad Serves",
      columns = 5:7) %>%
  tab_options(data_row.padding = px(15), column_labels.padding = px(7), column_labels.padding.horizontal = px(15), container.padding.y = px(15), heading.padding = px(7)) %>% 
  cols_align(align=c("center"),columns = everything())
gtserveplus1



##################################################################################################
##################################################################################################
##################################################################################################
################# PLEASE RUN THIS LAST COMMAND INTO YOUR CONSOLE TO GET THE IMAGE#################
##################################################################################################
##################################################################################################
##################################################################################################


### 
your_wd <- as.character(getwd())
gtsave(gtserveplus1, "serve+1.png", path = your_wd)
```


